High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-04 paper/main.tex
working on discussion-- added more summaries
corrected some typos and refs

\paragraph*{Event.} We generated a fourth set of 10 synthetic datasets
whose underlying correlation matrices exhibited prolonged intervals of
stability, intersperced with abrupt changes.  For each dataset, we
used Equation~\ref{fig:randcorr} to generate 5 random covariance
matrices.  We constructed a timeseries where each set of 60 consecutive samples
was drawn from a Gaussian with the same covariance matrix.  These
datasets were intended to simulate a system that undergoes occasional
abrupt state changes.

@@

Having established that patterns of high-order correlations are
informative to decoders, we next wondered which specific networks of
brain regions contributed most to these patterns.  As a representative
example, we selected the kernel parameters that yielded decoding
accuracies that best matched the average accuracies across all of the
kernel parameters we examined.  Using Figure~\ref{decoding}c as a
template, the best-matching kernel was a Laplace kernel with a width
of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
single $K$ by $K$ $n^\mathrm{th}$-order correlation matrix for each
experimental condition, along with the Neurosynth~\citep{RubiEtal17}
terms most highly associated with each of these matrices
(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).

@@

\item \cite{LuriEtal19}: review of time-varying connectivity

\item \cite{FongEtal18}: higher variability in dynamic functional connectivity
predicts worse attention.  also, dymamic functional connectivity
improves attention predictions over static functional connectivity.

\item \cite{ParkEtal17}: dynamic causal modelling: compute causal interaction
dynamics in multivariate timeseries data.  important to consider
causation in interpreting the direction of information flow reflected
in the patterns we identified through our analyses.

@@

\item \cite{RichEtal18}: simulations for benchmarking time-varying connectivity
methods (should we use this? seems useful! could potentially replace
synthetic data section)

\item \cite{ChanGlob09}

\item \cite{SizeEtal18}

>>>>

\paragraph*{Event.} We generated a fourth set of 10 synthetic datasets
whose underlying correlation matrices exhibited prolonged intervals of
stability, intersperced with abrupt changes.  For each dataset, we
used Equation~\ref{eqn:randcorr} to generate 5 random covariance
matrices.  We constructed a timeseries where each set of 60 consecutive samples
was drawn from a Gaussian with the same covariance matrix.  These
datasets were intended to simulate a system that undergoes occasional
abrupt state changes.

@@

Having established that patterns of high-order correlations are
informative to decoders, we next wondered which specific networks of
brain regions contributed most to these patterns.  As a representative
example, we selected the kernel parameters that yielded decoding
accuracies that best matched the average accuracies across all of the
kernel parameters we examined.  Using Figure~\ref{fig:decoding}c as a
template, the best-matching kernel was a Laplace kernel with a width
of 50 (Fig.~\ref{fig:kernels}d).  We used this kernel to compute a
single $K$ by $K$ $n^\mathrm{th}$-order correlation matrix for each
experimental condition, along with the Neurosynth~\citep{RubiEtal17}
terms most highly associated with each of these matrices
(Fig.~\ref{fig:neurosynth}; see \textit{Reverse inference}).

@@

\item \cite{LuriEtal18}: review of time-varying connectivity

\item \cite{FongEtal19}: higher variability in dynamic functional connectivity
predicts worse attention.  also, dymamic functional connectivity
improves attention predictions over static functional connectivity.

\item \cite{ParkEtal18b}: dynamic causal modelling: compute causal interaction
dynamics in multivariate timeseries data.  important to consider
causation in interpreting the direction of information flow reflected
in the patterns we identified through our analyses.

@@

\item \cite{ThomEtal18}: simulations for benchmarking time-varying connectivity
methods (should we use this? seems useful! could potentially replace
synthetic data section)

\item \cite{ChanGlov10}: early citation arguing that dynamic
  functional connectivity might contain valuable signal that is
  different from static functional connectivity.

\item \cite{SizeEtal18}:
